---
title: "preprocessing"
output:
  html_document: default
  pdf_document: default
---

```{r global}

library(pacman)
p_load(tidyverse, readr, tidyr, dplyr, paletteer, reasytries, strs, stringi, stringr, purrr, xtable, patchwork)
set.seed(123)

```

# Fish

## Preprocessing and Stats Table

```{r}

speciesList <- c('bre', 'mee', 'mul', 'oce', 'orn', 'pul')

# read data
dat <- read.csv("../fish-data/raw/PrettyDat.csv")

# fix a typo: mil should be mee
dat <- dat %>%
  mutate(species = recode(species, "mil" = "mee"))

#expand dat into sequences by trial_id, sequence_id, and fish_id
expanded <- dat %>%
  arrange(trial_id, sequence_id, order_id, fish_id, species) %>%
  group_by(trial_id, sequence_id, fish_id, species) %>%
  summarise(
  series = paste(rep(state, times = length), collapse = ""),
  .groups = "drop"
)

#series collapsed by repeats (e.g., "aaaabbbbccdddddccc" = "abcdc") to look at higher order patterns
expanded$col_series <- lapply(expanded$series, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))

#useful descriptive stats
statsTable <- expanded%>%
  group_by(species)%>%
  summarise(nSeq = n(),
             full_q3s = ceiling(quantile(nchar(series), 0.75)),
             col_q3s =  ceiling(quantile(nchar(col_series), 0.75)),
             fullMax = max(nchar(series)),
             colMax = max(nchar(col_series))
  )


```

## Ribbon Plots

### collapsed
```{r}

titleMap <- data.frame(old = c('bre', 'mee', 'mul', 'oce', 'orn', 'pul'),
                       new = c('N. brevis', 'L. meeli', 'N. multifasciatus', 'L. ocellatus', 'L. ornatipinnis', 'N. pulcher'))

plot_list <- list()

for (fish in speciesList) {
  
  fishDF <- expanded[expanded$species==fish,]
  
  strings <- unlist(fishDF$col_series)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  plot_list[[fish]] <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_col(width = 1) +
    scale_y_continuous(labels = scales::percent) +
    coord_cartesian(xlim = c(0, q3))+
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = titleMap$new[titleMap$old == fish]
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
}

combined_plot <-
  wrap_plots(plot_list, ncol = 2) +
  plot_layout(guides = "collect")

combined_plot
```





### full

```{r}

titleMap <- data.frame(old = c('bre', 'mee', 'mul', 'oce', 'orn', 'pul'),
                       new = c('N. brevis', 'L. meeli', 'N. multifasciatus', 'L. ocellatus', 'L. ornatipinnis', 'N. pulcher'))

plot_list <- list()

for (fish in speciesList) {
  
  fishDF <- expanded[expanded$species==fish,]
  
  strings <- unlist(fishDF$series)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  plot_list[[fish]] <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_col(width = 1) +
    scale_y_continuous(labels = scales::percent) +
    coord_cartesian(xlim = c(0, q3))+
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = titleMap$new[titleMap$old == fish]
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
}

combined_plot <-
  wrap_plots(plot_list, ncol = 2) +
  plot_layout(guides = "collect")

combined_plot
```


# Birds

## Preprocessing and Stats Tables

```{r prep}

#read in data
bird1 <- read.csv("../bird-data/raw/bird_1_df.csv")
bird2 <- read.csv("../bird-data/raw/bird_2_df.csv")
bird4 <- read.csv("../bird-data/raw/bird_4_df.csv")

### new birds :>
bird3 <- read.csv("../bird-data/raw/bird_3_df.csv")
bird5 <- read.csv("../bird-data/raw/bird_5_df.csv")
bird6 <- read.csv("../bird-data/raw/bird_6_df.csv")

# #bird id column
bird1$bird <- "bird1"
bird2$bird <- "bird2"
bird4$bird <- "bird4"
bird3$bird <- "bird3"
bird5$bird <- "bird5"
bird6$bird <- "bird6"

#unique syllables by bird
b1_syll <- unique(unlist(strsplit(bird1$song, "")))
b2_syll <- unique(unlist(strsplit(bird2$song, "")))
b3_syll <- unique(unlist(strsplit(bird3$song, "")))
b4_syll <- unique(unlist(strsplit(bird4$song, "")))
b5_syll <- unique(unlist(strsplit(bird5$song, "")))
b6_syll <- unique(unlist(strsplit(bird6$song, "")))

#---

#---
#all together
all <- list("1" = bird1, "2" = bird2, "3" = bird3, "4" = bird4, "5" = bird5, "6" = bird6)

#number of characters rotated
n <- 10

#target syllable to rotate from second instance, for each bird
targets <- c('a', 'c', 'i', 'b', 'b', 'h')

for (i in 1:length(all)) {
  
  dat <- all[[i]]
  
  #collapsed song
  dat$col_song <- lapply(dat$song, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))
  
  #reversed song (for suffixes)
  dat$rev_song <- lapply(dat$col_song, function(x) stri_reverse(unlist(x)))
  
  #random collapsed song
  dat$random_song <- sapply(dat$col_song, function(x) {paste0(sample(strsplit(x, "")[[1]]), collapse = "")})
  
  #nth-character rotated collapsed song
  dat$n_rot_song <- sapply(dat$col_song, function(x) {
    chars <- strsplit(x, "")[[1]]
    
    if (length(chars) < n) {
      return(NA)
    }
    
    paste0(
      paste0(chars[n:length(chars)], collapse = ""),
      paste0(chars[1:(n - 1)], collapse = "")
    )
  })
  
  #third instance of syllable rotated collapsed song
  target <- targets[i]
  
  dat$syll_rot_song <- sapply(dat$col_song, function(x) {
    chars <- strsplit(x, "")[[1]]
    positions <- which(chars == target)
    
    if (length(positions) < 3) {
      return(NA)
    }
    
    pos <- positions[3]
    paste0(
      paste0(chars[pos:length(chars)], collapse = ""),
      paste0(chars[1:(pos - 1)], collapse = "")
    )
  })
  
  all[[i]] <- dat
  
}

statsTable <- data.frame(bird = c('bird1', 'bird2', 'bird3', 'bird4', 'bird5', 'bird6'),
                          nSeq = c(nrow(all[[1]]), nrow(all[[2]]), nrow(all[[3]]), nrow(all[[4]]), nrow(all[[5]]), nrow(all[[6]])),
                          full_q1s = c(ceiling(quantile(nchar(all[[1]]$song), 0.25)),
                                       ceiling(quantile(nchar(all[[2]]$song), 0.25)),
                                       ceiling(quantile(nchar(all[[3]]$song), 0.25)),
                                       ceiling(quantile(nchar(all[[4]]$song), 0.25)),
                                       ceiling(quantile(nchar(all[[5]]$song), 0.25)),
                                       ceiling(quantile(nchar(all[[6]]$song), 0.25))),
                          full_q3s = c(ceiling(quantile(nchar(all[[1]]$song), 0.75)),
                                       ceiling(quantile(nchar(all[[2]]$song), 0.75)),
                                       ceiling(quantile(nchar(all[[3]]$song), 0.75)),
                                       ceiling(quantile(nchar(all[[4]]$song), 0.75)),
                                       ceiling(quantile(nchar(all[[5]]$song), 0.75)),
                                       ceiling(quantile(nchar(all[[6]]$song), 0.75))),
                          full_maxs = c(max(nchar(all[[1]]$song)),
                                      max(nchar(all[[2]]$song)),
                                      max(nchar(all[[3]]$song)),
                                      max(nchar(all[[4]]$song)),
                                      max(nchar(all[[5]]$song)),
                                      max(nchar(all[[6]]$song))),
                          col_q1s = c(ceiling(quantile(nchar(all[[1]]$col_song), 0.25)),
                                       ceiling(quantile(nchar(all[[2]]$col_song), 0.25)),
                                       ceiling(quantile(nchar(all[[3]]$col_song), 0.25)),
                                       ceiling(quantile(nchar(all[[4]]$col_song), 0.25)),
                                       ceiling(quantile(nchar(all[[5]]$col_song), 0.25)),
                                       ceiling(quantile(nchar(all[[6]]$col_song), 0.25))),
                          col_q3s = c(ceiling(quantile(nchar(all[[1]]$col_song), 0.75)),
                                       ceiling(quantile(nchar(all[[2]]$col_song), 0.75)),
                                       ceiling(quantile(nchar(all[[3]]$col_song), 0.75)),
                                       ceiling(quantile(nchar(all[[4]]$col_song), 0.75)),
                                       ceiling(quantile(nchar(all[[5]]$col_song), 0.75)),
                                       ceiling(quantile(nchar(all[[6]]$col_song), 0.75))), 
                          col_maxs = c(max(nchar(all[[1]]$col_song)),
                                      max(nchar(all[[2]]$col_song)),
                                      max(nchar(all[[3]]$col_song)),
                                      max(nchar(all[[4]]$col_song)),
                                      max(nchar(all[[5]]$col_song)),
                                      max(nchar(all[[6]]$col_song)))
                          )
```

## Ribbon Plots

One of the most important assumptions that my previous Markov sampling methods make is that of stationarity, i.e., the marginal state probability distribution remains constant over the length of the sequence. My methods compile transition probability tables over entire sequences, and lose any temporal information about transition probabilities. This works when sequences do not have a temporal element, but from a quick visual inspection, you can see this is NOT the case with these birds' songs--instead, there are common introductory sequences that are only present at the beginning of sequences. I generated these ribbon plots, which track the marginal state distributions by each time point, both for the full song version and the collapsed song version (where self-transitions are removed). 

You can see that there are strong regularities at the beginning of the plots, where each sequence position is dominated by one syllable. But after this, the state distributions even out. My intuition is that these songs can be viewed as two parts: one highly structured introductory sequence that rarely changes, and then afterwards a sequence that can be modeled by a Markov chain. However, I need to find a way to identify these regularities in a systematic rather than by eye. I decided to do this using an old technique from computer science: prefix tries!

Sanity checks for prefix identification:
[] random shuffling (random position per sequence)
[] nth occurence of syllable x in each sequence
[] position n in each sequence
  [] tagging intro to end should roughly reintroduce deterministic sequence later in ribbon plot?

```{r ribbons}

titleMap <- data.frame(
  old = c('bird1', 'bird2', 'bird3', 'bird4', 'bird5', 'bird6'),
  new = c('Bird 1', 'Bird 2', 'Bird 3', 'Bird 4', 'Bird 5', 'Bird 6')
)

for (col in c(2, 4, 5, 6, 7, 8)) {
  #for full song, collapsed song, reversed song, random song, n-rotated song, and syll-rotated song
  
  plot_list <- list()
  
  for (dat in all) {
    bird <- dat$bird[1]
    
    strings <- unlist(dat[, col])
    
    #split strings
    splitStrs <- strsplit(strings, "")
    
    #maximum length to pad with NAs
    maxL <- max(sapply(splitStrs, length))
    
    #long table of syllable by timepoint by sequence
    longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
      chars <- splitStrs[[i]]
      
      tibble(
        string_id = i,
        position = seq_len(maxL),
        character = c(chars, rep(NA, maxL - length(chars)))
      )
      
    }))
    
    ribbonDat <- longSeqs %>%
      group_by(position, character) %>%
      summarise(n = n(), .groups = "drop") %>%
      filter(!is.na(character)) %>%
      group_by(position) %>%
      mutate(proportion = n / sum(n)) %>%
      ungroup() %>%
      complete(position, character, fill = list(n = 0, proportion = 0))
    
    q3 <- ceiling(quantile(nchar(strings), 0.75, na.rm = TRUE)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
    
    plot_list[[bird]] <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
      #geom_col(width = 1) +
      geom_area() +
      scale_y_continuous(labels = scales::percent) +
      coord_cartesian(xlim = c(0, q3)) +
      labs(
        x = "Position",
        y = "Proportion",
        fill = "State",
        title = titleMap$new[titleMap$old == bird]
      ) +
      scale_fill_paletteer_d("rcartocolor::Prism") +
      theme_minimal()
    
  }
  
  combined_plot <-
    wrap_plots(plot_list, ncol = 2)
  
  print(combined_plot)
  
}

```


## Prefix Tries

Tries are a search tree data structure that encode and retrieve strings from dictionaries, in this case, our birdsong corpora. Each child node of this tree shares a common prefix with it;s parents, and in this way you can start to track common prefixes within the entire lexicon. I have compiled a trie for each bird's corpus, and then below, isolated prefixes from this trie that initiate more than 10% of songs. Ive set the maximum prefix length to 20 tokens, approximated from the max length of regularities from the ribbon plots (Bird 1, specifically). The resulting table identifies prefixes at most 20 tokens long (from the collapsed song version)

For reference: https://en.wikipedia.org/wiki/Trie

```{r tries}

trieCounts <- NULL

prefixLength = 40 #max prefix size to look for in trie, judged by longest ribbon plot regularities in all birds and all types of songs (this doesn't really matter as long as the search window is large enough)
for (col in c(4, 5, 6, 7, 8)) {
#for (col in c(8)) {
  
  #create prefix trie for each bird, compute proportions
  for (dat in all) {
    
    bird = dat$bird[1]
    
    #create a prefix trie
    trie <- trie_create()
    
    for (song in dat[, col]) {
      
      if (is.na(song))
        next
      
      prefix <- str_sub(song, 1, prefixLength) #take prefix of song at prefixLength
      trie_add(trie, prefix)
      
      #trie_add(trie, song) #add full song to trie instead
    }
    
    starts <- ls(trie@root@children) #first nodes of trie, i.e., the possible starting syllables
    
    tab <- NULL
    
    for (syl in starts) {
      unique_prefixes <- trie_find_prefix(trie, syl)
      
      for (pre in unique_prefixes) {
        temp <- data.frame(
          prefix = pre,
          count = sum(startsWith(unlist(dat[, col]), pre), na.rm = T),
          prop = sum(startsWith(unlist(dat[, col]), pre), na.rm = T) / sum(!is.na(dat[,col])),
          bird = bird,
          type = col
        )
        
        tab <- rbind(tab, temp)
        
      }
    }
    
    trieCounts <- rbind(trieCounts, tab)
    
  }
}

trieCounts$type <- recode(trieCounts$type, '4' = "collapsed", '5' = 'reversed', '6' = "random", '7' = "n-rot", '8' = "syll-rot")

```

## Cropped Sequences

I identified prefixes from the trie that occur in more than 10% of songs, by bird, and cropped these prefixes out of the songs.

```{r crop}
# identify deterministic prefixes occurring more than 20% of the time
cropTable <- trieCounts[(round(trieCounts$prop, 3)) >=.100,]

# crop out strong prefixes in normal songs

for (n in 1:length(all)){
  
  dat <- all[[n]]
  
  for (i in 1:nrow(dat)){
    
    col_song <- unlist(dat$col_song[i])
    song <- unlist(dat$song[i])
    
    bird <- dat$bird[1]
    birdTable <- cropTable[cropTable$bird == bird & cropTable$type == "collapsed",] #only use the normal collapsed prefixes
    
    #map which prefixes are present in song (vector is organized in alphabetically ordered nested prefixes, smallest size to longest size)
    bool <- as.integer(startsWith(col_song, birdTable$prefix))
    
    #if collapsed song contains prefix
    if (1 %in% bool) {
      
      prefix2crop <- birdTable$prefix[max(which(bool == 1))]
      dat$prefix[i] <- prefix2crop
      
      dat$cropped_col_song[i] <- strs_removeprefix(dat$col_song[i], prefix2crop)
      
      # --- simplified full-song cropping ---
      chars <- strsplit(song, "")[[1]]
      r <- rle(chars)
      collapsed_song <- paste0(r$values, collapse = "")
      
      pos <- regexpr(prefix2crop, collapsed_song)[1]
      
      if (pos == -1) {
        dat$cropped_song[i] <- song
      } else {
        end_collapsed <- pos + nchar(prefix2crop) - 1
        end_full <- cumsum(r$lengths)[end_collapsed]
        dat$cropped_song[i] <- substr(song, end_full + 1, nchar(song))
        dat$fullPrefix[i] <- substr(song, 1, end_full)
      }
      
    } else {
      
      dat$prefix[i] <- NA
      dat$cropped_col_song[i] <- dat$col_song[i]
      dat$cropped_song[i] <- dat$song[i]
      dat$fullPrefix[i] <- NA
      
    }
  }
  
  all[[n]] <- dat
}

prefixes <- na.omit(bind_rows(lapply(all, function(df) {
  df %>%
    select(bird, fullPrefix)
})))

croppedStats <- data.frame(bird = c('bird1', 'bird2', 'bird3', 'bird4', 'bird5', 'bird6'),
                           q1 = c(ceiling(quantile(nchar(all[[1]]$cropped_song), .25)),
                                  ceiling(quantile(nchar(all[[2]]$cropped_song), .25)),
                                  ceiling(quantile(nchar(all[[3]]$cropped_song), .25)),
                                  ceiling(quantile(nchar(all[[4]]$cropped_song), .25)),
                                  ceiling(quantile(nchar(all[[5]]$cropped_song), .25)),
                                  ceiling(quantile(nchar(all[[6]]$cropped_song), .25))
                                  ),
                           q3 = c(ceiling(quantile(nchar(all[[1]]$cropped_song), .75)),
                                  ceiling(quantile(nchar(all[[2]]$cropped_song), .75)),
                                  ceiling(quantile(nchar(all[[3]]$cropped_song), .75)),
                                  ceiling(quantile(nchar(all[[4]]$cropped_song), .75)),
                                  ceiling(quantile(nchar(all[[5]]$cropped_song), .75)),
                                  ceiling(quantile(nchar(all[[6]]$cropped_song), .75))
                                  )
)

```

### Save corpora

```{r save}

write.csv(prefixes,"../bird-data/prefixes.csv", row.names = FALSE)

for (dat in all){
  
  bird <- dat$bird[1]
  
  writeLines(dat$cropped_song, sprintf("../bird-data/raw/%s_cropped_full.txt", bird))
  writeLines(dat$song, sprintf("../bird-data/raw/%s_full.txt", bird))
  writeLines(unlist(dat$cropped_col_song), sprintf("../bird-data/raw/%s_cropped_collapsed.txt", bird))
  writeLines(unlist(dat$col_song), sprintf("../bird-data/raw/%s_collapsed.txt", bird))
  
}

```

### Cropped Ribbon Plots

Then I generated ribbon plots again of the cropped sequences. As you can see, they are much more stable! I am pretty confident that this section of the songs can be modeled well by my Markov chains. 

#### cropped full

```{r crop-rib}

titleMap <- data.frame(old = c('bird1', 'bird2', 'bird3', 'bird4', 'bird5', 'bird6'),
                       new = c('Bird 1', 'Bird 2', 'Bird 3', 'Bird 4', 'Bird 5', 'Bird 6'))

plot_list <- list()

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$cropped_song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  plot_list[[bird]] <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    #geom_col(width = 1) +
    geom_area()+
    scale_y_continuous(labels = scales::percent) +
    coord_cartesian(xlim = c(0, q3))+
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = titleMap$new[titleMap$old == bird]
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
}

combined_plot <-
  wrap_plots(plot_list, ncol =2)

combined_plot
```

#### cropped collapsed

```{r crop-rib-col}

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$cropped_col_song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75))
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    coord_cartesian(xlim = c(0, q3))+
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = bird
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```








