---
title: "preprocessing"
output:
  html_document: default
  pdf_document: default
---




```{r global}

library(pacman)
p_load(tidyverse, readr, tidyr, dplyr, paletteer, reasytries, strs, stringi, stringr, purrr)

```

# Fish

## Preprocessing and Stats Table

```{r}

speciesList <- c('bre', 'mil', 'mul', 'oce', 'orn', 'pul')

# read data
dat <- read.csv("../fish-data/raw/PrettyDat.csv")


#expand dat into sequences by trial_id, sequence_id, and fish_id
expanded <- dat %>%
  arrange(trial_id, sequence_id, order_id, fish_id, species) %>%
  group_by(trial_id, sequence_id, fish_id, species) %>%
  summarise(
  series = paste(rep(state, times = length), collapse = ""),
  .groups = "drop"
)

#series collapsed by repeats (e.g., "aaaabbbbccdddddccc" = "abcdc") to look at higher order patterns
expanded$col_series <- lapply(expanded$series, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))

#useful descriptive stats
statsTable <- expanded%>%
  group_by(species)%>%
  summarise(nSeq = nrow(species),
             full_q3s = ceiling(quantile(nchar(series), 0.75)),
             col_q3s =  ceiling(quantile(nchar(col_series), 0.75)),
             fullMax = max(nchar(series)),
             colMax = max(nchar(col_series))
  )


```

## Ribbon Plots

### collapsed
```{r}


for (fish in speciesList) {
  
  fishDF <- expanded[expanded$species==fish,]
  
  strings <- unlist(fishDF$col_series)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = fish
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```
# full

```{r}


for (fish in speciesList) {
  
  fishDF <- expanded[expanded$species==fish,]
  
  strings <- unlist(fishDF$series)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = fish
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```


# Birds

## Preprocessing and Stats Tables

```{r prep}

#read in data
bird1 <- read.csv("../bird-data/raw/bird_1_df.csv")
bird2 <- read.csv("../bird-data/raw/bird_2_df.csv")
bird4 <- read.csv("../bird-data/raw/bird_4_df.csv")

# #bird id column
bird1$bird <- "bird1"
bird2$bird <- "bird2"
bird4$bird <- "bird4"

#songs collapsed by repeats (e.g., "aaaabbbbccdddddccc" = "abcdc") to look at higher order patterns
bird1$col_song <- lapply(bird1$song, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))
bird2$col_song <- lapply(bird2$song, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))
bird4$col_song <- lapply(bird4$song, function(x) paste(rle(unlist(strsplit(x,"")))$values, collapse = ""))

#---
#useful descriptive stats
statsTable <- data.frame(bird = c('bird1', 'bird2', 'bird4'),
                         nSeq = c(nrow(bird1), nrow(bird2), nrow(bird4)),
                         full_q3s = c(ceiling(quantile(nchar(bird1$song), 0.75)),
                                 ceiling(quantile(nchar(bird2$song), 0.75)),
                                 ceiling(quantile(nchar(bird4$song), 0.75))),
                         col_q3s = c(ceiling(quantile(nchar(bird1$col_song), 0.75)),
                                 ceiling(quantile(nchar(bird2$col_song), 0.75)),
                                 ceiling(quantile(nchar(bird4$col_song), 0.75))),
                         full_max = c(max(nchar(bird1$song)),
                                     max(nchar(bird2$song)),
                                     max(nchar(bird4$song))),
                         col_max = c(max(nchar(bird1$col_song)),
                                     max(nchar(bird2$col_song)),
                                     max(nchar(bird4$col_song)))
                         )

#unique syllables by bird
b1_syll <- unique(unlist(strsplit(bird1$song, "")))
b2_syll <- unique(unlist(strsplit(bird2$song, "")))
b4_syll <- unique(unlist(strsplit(bird4$song, "")))

#---
#all together
all <- list("1" = bird1, "2" = bird2, "4" = bird4)

```

## Ribbon Plots

One of the most important assumptions that my previous Markov sampling methods make is that of stationarity, i.e., the marginal state probability distribution remains constant over time. My methods compile transition probability tables over entire sequences, and lose any temporal information about transition probabilities. This works when sequences do not have a temporal element, but from a quick visual inspection, you can see this is NOT the case with these birds' songs--instead, there are common introductory sequences that are only present at the beginning of sequences. I generated these ribbon plots, which track the marginal state distributions by each time point, both for the full song version and the collapsed song version (where self-transitions are removed). 

You can see that especially for birds 1 and 4, there are strong regularities at the beginning of the plots, where each time step is dominated by one syllable. But after this, the state distributions even out. My intuition is that these songs can be viewed as two parts: one highly structured introductory sequence that rarely changes, and then afterwards a sequence that can be modeled by a Markov chain. However, I need to find a way to identify these regularities in a systematic rather than by eye. I decided to do this using an old technique from computer science: prefix tries!

### collapsed songs
```{r ribbons-col}

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$col_song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table of syllable by timepoint by sequence
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75)) #use q3 length as cut-off point because sequences are variable length, and long outlier sequences heavily bias end of ribbon plot
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = bird
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}

```

### full songs

```{r ribbons-full}

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75))
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = bird
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```

(I also wanted to see whether there were regularities at the ends of songs, like suffixes. These patterns are not as strong and further trie analyses did not identify anything particularly strong)



## Prefix Tries

Tries are a search tree data structure that encode and retrieve strings from dictionaries, in this case, our birdsong corpora. Each child node of this tree shares a common prefix with it;s parents, and in this way you can start to track common prefixes within the entire lexicon. I have compiled a trie for each bird's corpus, and then below, isolated prefixes from this trie that initiate more than 10% of songs. Ive set the maximum prefix length to 20 tokens, approximated from the max length of regularities from the ribbon plots (Bird 1, specifically). The resulting table identifies prefixes at most 20 tokens long (from the collapsed song version)

For reference: https://en.wikipedia.org/wiki/Trie

```{r tries}

trieCounts <- NULL

prefixLength = 20 #max prefix size to look for in trie, judged by longest ribbon plot regularities in all birds (~20 from Bird 1)

#create prefix trie for each bird, compute proportions
for (dat in all) {
  
  bird = dat$bird[1]
  
  #create a prefix trie
  trie <- trie_create()
  
  for (song in dat$col_song) {
    
    prefix <- str_sub(song, 1, prefixLength) #take prefix of song at prefixLength 
    trie_add(trie, prefix)
    
    #trie_add(trie, song) #add full song to trie instead
  }

  
  starts <- ls(trie@root@children) #first nodes of trie, i.e., the possible starting syllables
  
  tab <- NULL
  
  for (syl in starts) {
    
    unique_prefixes <- trie_find_prefix(trie, syl)
    
    for (pre in unique_prefixes) {
      
      temp <- data.frame(
        prefix = pre,
        count = sum(startsWith(unlist(dat$col_song), pre)),
        prop = sum(startsWith(unlist(dat$col_song), pre)) / nrow(dat),
        bird = bird
      )
      
      tab <- rbind(tab, temp)
      
    }
  }
  
  trieCounts <- rbind(trieCounts, tab)
  
}

```

## Cropped Sequences

I identified prefixes from the trie that occur in more than 10% of songs, by bird, and cropped these prefixes out of the songs.

```{r crop}
# identify deterministic prefixes occurring more than 10% of the time
cropTable <- trieCounts[(round(trieCounts$prop, 2)) >=.10,]

# crop out strong prefixes in birds 1 and 4 (2 doesn't have any)

for (n in 1:length(all)){
  
  dat <- all[[n]]
  
  for (i in 1:nrow(dat)){
    
    col_song <- unlist(dat$col_song[i])
    song <- unlist(dat$song[i])
    
    #map which prefixes are present in song (vector is organized in alphabetically ordered nested prefixes, smallest size to longest size)
    bool <- as.integer(startsWith(col_song, cropTable$prefix))
    
    #if collapsed song contains prefix
    if (1 %in% bool) {
      
      prefix2crop <- cropTable$prefix[max(which(bool == 1))]
      dat$prefix[i] <- prefix2crop
      
      dat$cropped_col_song[i] <- strs_removeprefix(dat$col_song[i], prefix2crop)
      
      # --- simplified full-song cropping ---
      chars <- strsplit(song, "")[[1]]
      r <- rle(chars)
      collapsed_song <- paste0(r$values, collapse = "")
      
      pos <- regexpr(prefix2crop, collapsed_song)[1]
      
      if (pos == -1) {
        dat$cropped_song[i] <- song
      } else {
        end_collapsed <- pos + nchar(prefix2crop) - 1
        end_full <- cumsum(r$lengths)[end_collapsed]
        dat$cropped_song[i] <- substr(song, end_full + 1, nchar(song))
        dat$fullPrefix[i] <- substr(song, 1, end_full)
      }
      
    } else {
      
      dat$prefix[i] <- NA
      dat$cropped_col_song[i] <- dat$col_song[i]
      dat$cropped_song[i] <- dat$song[i]
      dat$fullPrefix[i] <- NA
      
    }
  }
  
  all[[n]] <- dat
}

prefixes <- na.omit(bind_rows(lapply(all, function(df) {
  df %>%
    select(bird, fullPrefix)
})))

write.csv(prefixes,"../bird-data/prefixes.csv", row.names = FALSE)

```

## Save corpora

```{r save}

for (dat in all){
  
  bird <- dat$bird[1]
  
  writeLines(dat$cropped_song, sprintf("../bird-data/raw/%s_cropped_full.txt", bird))
  writeLines(dat$song, sprintf("../bird-data/raw/%s_full.txt", bird))
  writeLines(unlist(dat$cropped_col_song), sprintf("../bird-data/raw/%s_cropped_collapsed.txt", bird))
  writeLines(unlist(dat$col_song), sprintf("../bird-data/raw/%s_collapsed.txt", bird))
  
}

```

## Cropped Ribbon Plots

Then I generated ribbon plots again of the cropped sequences. As you can see, they are much more stable! I am pretty confident that this section of the songs can be modeled well by my Markov chains. 

### cropped full

```{r crop-rib}

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$cropped_song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75))
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = bird
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```

### cropped collapsed

```{r crop-rib-col}

for (dat in all) {
  
  bird <- dat$bird[1]
  
  strings <- unlist(dat$cropped_col_song)
  
  #split strings
  splitStrs <- strsplit(strings, "")
  
  #maximum length to pad with NAs
  maxL <- max(sapply(splitStrs, length))
  
  #long table
  longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
    chars <- splitStrs[[i]]
    
    tibble(
      string_id = i,
      position = seq_len(maxL),
      character = c(chars, rep(NA, maxL - length(chars)))
    )
    
  }))
  
  ribbonDat <- longSeqs %>%
  group_by(position, character) %>%
  summarise(n = n(), .groups = "drop") %>%
  filter(!is.na(character)) %>%
  group_by(position) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup() %>%
  complete(
    position,
    character,
    fill = list(n = 0, proportion = 0)
  )
  
  q3 <- ceiling(quantile(nchar(strings), 0.75))
  
  p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
    geom_area() +
    scale_y_continuous(labels = scales::percent) +
    scale_x_continuous(limits = c(0, q3)) +
    labs(
      x = "Position",
      y = "Proportion",
      fill = "State",
      title = bird
    ) +
    scale_fill_paletteer_d("rcartocolor::Prism") +
    theme_minimal()
  
  print(p)
  
}
```



# Appendix: Suffixes in Birdsong

## backwards ribbon plots collapsed

```{r back-ribbons-col}

# for (dat in all) {
#   
#   bird <- dat$bird[1]
#   
#   stringsrev <- stri_reverse(unlist(dat$col_song))
#   
#   #split strings
#   splitStrs <- strsplit(stringsrev, "")
#   
#   #maximum length to pad with NAs
#   maxL <- max(sapply(splitStrs, length))
#   
#   #long table
#   longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
#     chars <- splitStrs[[i]]
#     
#     tibble(
#       string_id = i,
#       position = seq_len(maxL),
#       character = c(chars, rep(NA, maxL - length(chars)))
#     )
#     
#   }))
#   
#   ribbonDat <- longSeqs %>%
#   group_by(position, character) %>%
#   summarise(n = n(), .groups = "drop") %>%
#   filter(!is.na(character)) %>%
#   group_by(position) %>%
#   mutate(proportion = n / sum(n)) %>%
#   ungroup() %>%
#   complete(
#     position,
#     character,
#     fill = list(n = 0, proportion = 0)
#   )
#   
#   p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
#     geom_area() +
#     scale_y_continuous(labels = scales::percent) +
#     scale_x_continuous(limits = c(0, 30)) +
#     labs(
#       x = "Position",
#       y = "Proportion",
#       fill = "State",
#       title = bird
#     ) +
#     scale_fill_paletteer_d("rcartocolor::Prism") +
#     theme_minimal()
#   
#   print(p)
#   
# }

```

## backwards ribbon plots full

```{r back-ribbons-full}

# for (dat in all) {
#   
#   bird <- dat$bird[1]
#   
#   stringsrev <- stri_reverse(unlist(dat$song))
#   
#   #split strings
#   splitStrs <- strsplit(stringsrev, "")
#   
#   #maximum length to pad with NAs
#   maxL <- max(sapply(splitStrs, length))
#   
#   #long table
#   longSeqs <- bind_rows(lapply(seq_along(splitStrs), function(i) {
#     chars <- splitStrs[[i]]
#     
#     tibble(
#       string_id = i,
#       position = seq_len(maxL),
#       character = c(chars, rep(NA, maxL - length(chars)))
#     )
#     
#   }))
#   
#   ribbonDat <- longSeqs %>%
#   group_by(position, character) %>%
#   summarise(n = n(), .groups = "drop") %>%
#   filter(!is.na(character)) %>%
#   group_by(position) %>%
#   mutate(proportion = n / sum(n)) %>%
#   ungroup() %>%
#   complete(
#     position,
#     character,
#     fill = list(n = 0, proportion = 0)
#   )
#   
#   q3 <- ceiling(quantile(nchar(stringsrev), 0.75))
#   
#   p <- ggplot(ribbonDat, aes(x = position, y = proportion, fill = character)) +
#     geom_area() +
#     scale_y_continuous(labels = scales::percent) +
#     scale_x_continuous(limits = c(0, q3)) +
#     labs(
#       x = "Position",
#       y = "Proportion",
#       fill = "State",
#       title = bird
#     ) +
#     scale_fill_paletteer_d("rcartocolor::Prism") +
#     theme_minimal()
#   
#   print(p)
#   
# }

```

## Suffix Tries

```{r suffix-tries}

# trieCountsSuffix <- NULL
# 
# suffixLength = 15 #max prefix size to look for in trie
# 
# #create prefix trie for each bird, compute proportions
# for (dat in all) {
#   
#   bird = dat$bird[1]
#   dat$rev_song <- stri_reverse(unlist(dat$col_song)) 
#   
#   #create a prefix trie
#   trie <- trie_create()
#   
#   for (song in dat$rev_song) {
#     
#     suffix <- str_sub(song, 1, suffixLength) #take prefix of song at prefixLength 
#     trie_add(trie, suffix)
#     
#     #trie_add(trie, song) #add full song to trie instead
#   }
# 
#   
#   ends <- ls(trie@root@children) #first nodes of trie, i.e., the possible starting syllables
#   
#   tab <- NULL
#   
#   for (syl in ends) {
#     
#     unique_suffixes <- trie_find_prefix(trie, syl)
#     
#     for (suf in unique_suffixes) {
#       
#       temp <- data.frame(
#         suffix = suf,
#         count = sum(startsWith(unlist(dat$rev_song), suf)),
#         prop = sum(startsWith(unlist(dat$rev_song), suf)) / nrow(dat),
#         bird = bird
#       )
#       
#       tab <- rbind(tab, temp)
#       
#     }
#   }
#   
#   trieCountsSuffix <- rbind(trieCountsSuffix, tab)
#   
# }


#cropTableSuffix <- trieCountsSuffix[(round(trieCountsSuffix$prop, 2)) >=.10,]
```